Future challenges for Research Software Engineering

### 2025-09-24 future_challenges_for_RSEng.tex
be more assertive

So where do RSEs fit into this picture?
Even today, we expect to see RSEs providing technical skills and input to research activities in a range of different areas, including:
high-quality, robust architecture and design for research software;
seamless integration with research and data infrastructures;
development of software for novel and emerging architectures;
application of specialist numerical and statistical methods within software;
optimisation of codes for use on high-performance computing infrastructure;
and green computing - efficient implementations of algorithms/methods and use of hardware.
These specialist skills that RSEs provide take a significant amount of time to develop and maintain,
which is why we do not expect domain researchers to also become experts in a range of advanced RSEng topics.

>>>>

So where do RSEs fit into this picture?
Already today, RSEs are providing technical skills and input to research activities in a range of different areas, including:
high-quality, robust architecture and design for research software;
seamless integration with research and data infrastructures;
development of software for novel and emerging architectures;
application of specialist numerical and statistical methods within software;
optimisation of codes for use on high-performance computing infrastructure;
and green computing - efficient implementations of algorithms/methods and use of hardware.
These specialist skills that RSEs provide take a significant amount of time to develop and maintain,
which is why we do not expect domain researchers to also become experts in a range of advanced RSEng topics.
